\documentclass[9pt]{article}
\usepackage[a4paper,margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\titleformat{\section}{\normalsize\bfseries\scshape}{}{0em}{}
\renewcommand{\labelitemi}{\textbullet}
\setlist[itemize]{left=0pt, labelsep=0.5em, itemsep=0.2em, top=0.2em}
\pagenumbering{gobble}
\begin{document}
\small

% Header
\begin{minipage}[t]{0.6\textwidth}
  {\LARGE\textbf{Hritik Gupta}} \\
  \vspace{2pt}
  \href{https://www.linkedin.com/in/hritik-gupta-ml/}{\textcolor{blue}{Linkedin: https://www.linkedin.com/in/hritik-gupta-ml/}} \\
  \href{https://github.com/hritikgupta01}{\textcolor{blue}{Github: https://github.com/hritikgupta01}}
\end{minipage}%
\begin{minipage}[t]{0.4\textwidth}
  \raggedleft
  Email : \href{mailto:hritik3696@gmail.com}{hritik3696@gmail.com} \\
  Mobile : +91-953-211-5855
\end{minipage}

\vspace{0.5em}

% Skills Summary
\section*{Skills Summary}
\textbf{Languages:} Java, Python, SQL, JavaScript \\
\textbf{Frameworks:} Flask, NodeJs, \\
\textbf{Tools:} GIT, MongoDB, MySQL, SQLite, ReactJs, Aws EC2, ExpressJs \\
\textbf{Platforms:} Linux, Windows, Web, Arduino, Raspberry \\
\textbf{Soft Skills:} Leadership, Directorate, Writing, Time Management

% Education
\section*{Education}
\textbf{Noida Institute of Engineering and Technology} \hfill Greater Noida, Up, India \\
\textit{Bachelor in Computer Science and Engineering with Artificial Intelligence; GPA: 8.54} \hfill Nov 2020 - May 2024 \\
\textit{Courses: Operating Systems, Data Structures, Analysis Of Algorithms, Machine Learning, Networking, Databases, Web Development}

% Experience
\section*{Experience}
\textbf{iNeuron} \hfill Bengaluru, India \\
\textit{Software Developer Engineer Intern} \hfill Mar 2023 - Apr 2023
\begin{itemize}
  \item Created a regression model for \textbf{Metro Interstate Traffic Volume} forecasting with a low \textbf{RMSE of 0.37}.
  \item Experience in performing data analysis using Python, NumPy, Pandas, Scikit-Learn, and Jupyter.
  \item Performed data cleaning, preprocessing, exploratory, and deep dive analysis to fetch meaningful insights.
  \item Tested and Validated \textbf{CatBoostRegressor}, \textbf{AdaBoostRegressor}, and \textbf{XGBRegressor} to determine the optimal model. \textbf{CatBoostRegressor} 17\% more accurate than others.
  \item Skilled in creating documents LLD, HLD, using Azure DevOps.
\end{itemize}

\textbf{Noida Institute of Engineering and Technology} \hfill Greater Noida, India \\
\textit{Machine Learning Engineer Intern} \hfill Sep 2022 - Nov 2022
\begin{itemize}
  \item Developed a Calling Bot solution that effectively updated parents on their child’s attendance with a 99\% success rate, significantly reducing workload by 80\%.
  \item Facilitated over 1500+ calls, in significant time savings and improved efficiency.
  \item Developed the software using Python and leveraged Twilio API to enable backend calling functionality. Utilized AWS EC2 for deployment and SQLite for data storage.
\end{itemize}

\textbf{IDR Research and Development Pvt. Ltd} \hfill Greater Noida, India \\
\textit{Machine Learning Engineer Intern} \hfill Nov 2021 - May 2022
\begin{itemize}
  \item Implemented and integrated Drone (UAVs) with COMPUTER VISION applications involving vehicle plate recognition, image segmentation, Real-time object tracking and person detection.
  \item Led team to achieve 20\% increase in FPS for object detection and reducing action time to 0.05ms through image segmentation for decision making.
  \item Utilized Python, MobileNet, Darknet, YOLOv5, YOLO7, OpenCV, TensorFlow, Torch, and Raspberry Pi for image processing and computer vision tasks.
\end{itemize}

% Projects
\section*{Projects}
\begin{itemize}
  \item Chat application (\textbf{link:} \href{https://m-talk.onrender.com/}{https://m-talk.onrender.com/}): Developed a robust chat application using ReactJS, NodeJS, ExpressJS, MongoDB, SocketIO, and Chakra UI. Implemented real-time messaging with user authentication and secured data storage. Leveraged Render server for seamless deployment and scalability.
  \item Digit Image Generator - GAN (\textbf{link:} \href{https://hritikguptagan.pythonanywhere.com/}{https://hritikguptagan.pythonanywhere.com/}): Developed GANs using Python, OpenCV, TensorFlow, and Keras to generate digit images for data augmentation, leading to a 20\% improvement in model accuracy after 100,000 epochs on a 60,000-image MNIST digit dataset.
  \item Movie Recommendation System (\textbf{link:} \url{https://hritik211.pythonanywhere.com/movie_recommend/}): Created a content-based movie recommendation system with a 92\% accuracy rate using Python, NLP, Flask, and Pythonanywhere, resulting in a 60\% increase in user retention.
  \item Gender Predictor API (\textbf{link:} \href{https://tinyurl.com/2ufznfaj}{https://tinyurl.com/2ufznfaj}): Designed to predict the gender based on name.
\end{itemize}

% Honors and Awards
\section*{Honors And Awards}
\begin{itemize}
  \item Impressively solved over 700 DSA problems on LeetCode, GFG, and HackerRank.
  \item Ranked among the top 50 in problem-solving on Geek for Geeks out of 3100 participants.
  \item Winner of Sharda University’s 2022 Tech Pitch championship.
\end{itemize}

% Certifications
\section*{Certifications}
CodeStudio’s technical interview Guide for product-based companies: offers valuable insights and resources for building AI-powered applications.

\end{document}