\documentclass[10pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage[left=0.75in, right=0.75in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{tikz}

\pagestyle{empty} % No page numbers

% Custom commands for consistency
\newcommand{\sectiontitle}[1]{\vspace{6pt}\hrule height 1pt \vspace{3pt}\textbf{\large #1}\vspace{3pt}\hrule height 0.5pt \vspace{6pt}}
\newcommand{\subsectionitem}[3]{\textbf{#1} \hfill \textit{#2} \\ #3}
\newcommand{\projectitem}[3]{\textbf{#1} \hfill \textit{#2} \\ #3}

\begin{document}

\begin{center}
    \textbf{\huge Pranjal Mishra} \\
    \vspace{2pt}
    \small \faPhoneExtender \ +91-8858641124 \textperiodcentered\ \faEnvelope \ pranjalnitjsr@gmail.com \textperiodcentered\ \href{https://www.linkedin.com/in/pranjal-mishra-profile}{\faLinkedin \ LinkedIn} \textperiodcentered\ \href{https://github.com/pranjalmishra}{\faGithub \ GitHub}
\end{center}

\sectiontitle{EDUCATION}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt}
\begin{itemize}
    \item \subsectionitem{National Institute of Technology, Jamshedpur}{Jharkhand, India}{}
          B.Tech in Production and Industrial Engineering CGPA: 8.02 \hfill \textit{Nov 2022 -- July 2026}
    \item \subsectionitem{St. Xavier's Senior Secondary School, Kannauj}{Uttar Pradesh, India}{}
          Class 12th CBSE Percentage: 94 \hfill \textit{April 2020 -- April 2021}
\end{itemize}

\sectiontitle{EXPERIENCE}
\begin{itemize}
    \item \subsectionitem{Retech Technologies}{Jan 2025 -- Feb 2025}{}
          \textbf{Backend Developer Intern}
          \begin{itemize}
              \item Developed scalable REST APIs for third-party integrations, enabling secure data sharing. [cite: 2]
              \item Integrated payment gateways and automated receipt generation processes. [cite: 2]
              \item Built seller management dashboards for tracking orders and monitoring shipping status. [cite: 2]
          \end{itemize}
\end{itemize}

\sectiontitle{PROJECTS}
\begin{itemize}
    \item \projectitem{Magnews (Full-Stack Blogging and News Web App)}{\textit{View Code} \textperiodcentered\ \textit{Website}}{June 2024}
          \textbf{Tech Stack:} ReactJS, Node.js, Express.js, MongoDB, Firebase, Tailwind CSS
          \begin{itemize}
              \item Built a dynamic platform for publishing, reading, and managing articles. [cite: 4]
              \item Integrated Firebase Authentication for secure login and notifications. [cite: 4]
              \item Designed an admin dashboard for analytics and engagement tracking, reducing content moderation time by 25%. [cite: 5]
          \end{itemize}
    \item \projectitem{Aviation Team Website}{\textit{View Code} \textperiodcentered\ \textit{Website}}{May 2024}
          \textbf{Tech Stack:} ReactJS, NodeJS, Express.js, Firebase, Tailwind CSS, Vite
          \begin{itemize}
              \item Developed a dynamic site to showcase projects, events, and sponsors. [cite: 6]
              \item Automated email confirmations upon user registration. [cite: 6]
              \item Created a responsive UI using Tailwind CSS and ReactJS. [cite: 7]
          \end{itemize}
    \item \projectitem{Smart India Hackathon Project}{\textit{View Code} \textperiodcentered\ \textit{Website}}{May 2024}
          \textbf{Tech Stack:} ReactJS, NodeJS, Express.js, MongoDB, Firebase
          \begin{itemize}
              \item Built a prototype dashboard for team submissions and mentor feedback. [cite: 8]
              \item Simulated real-world problem solving from SIH challenge. [cite: 8]
          \end{itemize}
\end{itemize}

\sectiontitle{RELEVANT COURSEWORK}
\begin{itemize}
    \item DSA
    \item Database Management
    \item Cyber Security
    \item MERN Stack
    \item System Design
    \item Firebase
\end{itemize}

\sectiontitle{SKILLS}
\begin{itemize}
    \item \textbf{Languages:} C++, JavaScript (ES6+), HTML/CSS
    \item \textbf{Frameworks:} ReactJS, Node.js, Express.js, Django
    \item \textbf{Databases:} MongoDB, Firebase, PostgreSQL
    \item \textbf{Tools:} Docker, Git, GitHub, Vercel, GCP, VS Code, Postman
    \item \textbf{Other:} REST APIs, API Design, Microservices, Firebase Auth, CI/CD, Responsive Design, Problem Solving
\end{itemize}

\sectiontitle{ACHIEVEMENTS}
\begin{itemize}
    \item Web Development Lead at Google Developers Student Club, NIT Jamshedpur
    \item Web Development Head at Team Phoenix, NIT Jamshedpur
    \item Completed intermediate-level Google Cybersecurity course on Coursera (June 2024)
    \item Among top 5 teams of the university in Smart India Hackathon 2024
    \item Solved 700+ Competitive Programming problems on Codeforces, LeetCode, and CodeChef [cite: 9]
\end{itemize}

\end{document}